---
title: "ML_Documentation"
author: "Geiser Silvia, Gruen Markus, Hefti Nico, Kuster Thomas"
date: "10/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Machine Learning Algorithms - Documentation 

---
date: '10/17/2020'
author: Silvia Geiser
main changes: load raw data, data cleaning
---
load raw dataset
```{r}
rawdata <- read.csv('germany_housing_original_data.csv', header = T, row.names = 'X')
head(rawdata)
```

see data
```{r}
dim(rawdata)
```


drop columns (Usable_area, Free_of_Relation, Energy_certificate, Energy_certificate_type, Energy_consumption) from raw data
```{r}
data <- subset(rawdata, select = -c(Usable_area, Free_of_Relation, Energy_certificate, Energy_certificate_type, Energy_consumption))
head(data)
dim(data)
colnames(data)
```

see datatypes
```{r}
#install.packages('dplyr')
library(dplyr)
glimpse(data)
```

summary of data
```{r}
print(summary(data))
```
extract rows with Year_renovated > 2020 and replace with NA
```{r}
data %>%
filter(Year_renovated > 2020)

data <- data %>% mutate(Year_renovated = replace(Year_renovated, Year_renovated > 2020, NA))
```

extract rows with Year_built > 2020 and replace with NA
```{r}
data %>%
filter(Year_built > 2020)

data <- data %>% mutate(Year_built = replace(Year_built, Year_built > 2020, NA))
```

see data and summary
```{r}
head(data)
print(summary(data))
```
extract unique values in Heating
```{r}
unique(data$Heating)
```

extract unique values in Energy_source

```{r}
unique(data$Energy_source)
```
group and clean up Energy_source categories
```{r}
install.packages(plyr)
data1 <- data
data1$Energy_source <- revalue(data1$Energy_source, c(" Öl " = 'oil', ))
head(a)


find data with < 10.00 Living_space and drop rows
```{r}
data %>%
arrange(data$Living_space)
which(data$Living_space < 10.0)
data1 <- data %>% slice(-c(344,7738,8177,9822,9956))
data <- data1
head(data)
```


find rows with price 0

```{r}
data %>%
arrange(data$Price)
which(data$Price > 10000 & data$Price < 15000)
data[c(80, 84, 328, 460, 2971,3189, 3192, 3783, 4688, 5069, 5707, 5708, 5709, 5774, 6079, 6661, 6987, 7591,7656, 7838, 7859, 7997, 8617, 8738, 8868, 8874, 9001, 9019, 9100, 9378, 9681, 9755, 9777, 9936, 9974, 10352),]

data[c(2914,  3191,  6837,  7943,  9044,  9144,  9467,  9518,  9611,  9658,  9667,  9723,  9791,  9792,  9798,  9799, 10475),]
```